### 2014-06-29 Choosing R3 Relations.tex
edited_todo
Possible 4.2 Analogue

An equivlent relation is as follows

@@

\begin{lem}
The relation r(a,a+1) for some vertex a $\in$ C implies the relation r(b, b+1) for all b $\in$ C.
\end{lem}
\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}

@@

\begin{thm}
\label{square_mutation_preserved}
The relations described in ~\ref{even_more_relations} are permuted (and hence preserved) after mutation at any vertex.
\end{thm}
\begin{proof}
This is what additionally needs to be checked in ~\ref{5.2 analog} by adding ~\ref{even_more_relations} in the cases corresponding to cycles with edges of weight 2 in the paper. I.e. it has to be checked in cases (b,c,d,e,f,g,h). It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out. 
\end{proof}

>>>>

An equivalent relation is as follows

@@

\begin{lem} (Analogue of 4.1)
The relation r(a,a+1) for some vertex a $\in$ C implies the relation r(b, b+1) for all b $\in$ C.
\end{lem}
\begin{proof}
As in Barot-Marsh, it suffices to prove that the relation r(0, 1) implies the relation r(d-1, 0). So suppose $W_{\gamma}$ satisfies the relation r(0, 1). Then we have 
\begin{align*}
& s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_1s_0 \\
&= s_{0}^{-1}s_{0}s_{d-1}s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{d-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{1}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{0}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{1})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-2}^{-1}s_{d-1}s_{d-2}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{d-1}^{-1}(s_{1}^{-1} \dots s_{d-3}^{-1}s_{d-1}s_{d-2}s_{d-1}^{-1}s_{d-3}\dots s_{0})s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{d-1}^{-1}s_{0}s_{d-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1}s_{0}^{-1}s_{0} \\
&= s_{0}^{-1}s_{1}^{-1}\dots s_{d-3}^{-1}s_{d-2}s_{d-3}\dots s_{1}s_{0}s_{d-1} 
\end{align*}
as required. Note that line 3 is equal to 4 and line 7 is equal to line 8 since the cycle is chordless, meaning that $s_{d-1}$ commutes with every element except $s_{0}$ and $s_{d-2}$.
\end{proof}

\begin{defn} (Possible relations for the weight 2 triangle) Given the cycle in Figure 8 of Barot-Marsh, we define the following relations
\begin{enumerate}[(a)]
\item $s_{1}s_{2}^{-1}s_{3}s_{2} = s_{2}^{-1}s_{3}s_{2}s_{1}$
\item $s_{2}s_{3}^{-1}s_{1}s_{3} = s_{3}^{-1}s_{1}s_{3}s_{2}$
\item $s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1} = e$
\end{enumerate}
\end{defn}

\begin{lem} (Analogue of 4.2)
In the above definition, if the generators satisfy the relations (R2'), then the relations (a) and (b) are equivalent, and the relations (a) and (b) imply the relation (c).
\end{lem}

\begin{proof}
I haven't worked out the equivalence of (a) and (b) yet, so I'll leave it for someone else.

In showing that (a) and (b) imply (c), I will underline the terms being manipulated in each line for emphasis.
\begin{align*}
& s_{1}s_{3}s_{1}(s_{3}^{-1}s_{1}^{-1}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{1})s_{1}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}\underline{s_{1}s_{1}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
&= \underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}\underline{s_{3}^{-1}s_{1}s_{3}s_{1}}s_{3}s_{1}^{-1}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}s_{1}s_{3}\underline{s_{1}s_{3}^{-1}s_{3}s_{1}^{-1}}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}\underline{e}s_{1}s_{3}s_{2}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{2}s_{3}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= \underline{s_{2}s_{3}s_{2}}s_{3}^{-1}s_{1}s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}s_{2}\underline{s_{3}s_{3}^{-1}}s_{1}\underline{s_{3}s_{1}s_{3}^{-1}s_{1}^{-1}}s_{2}^{-1}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}s_{2}\underline{s_{1}s_{1}^{-1}}\underline{s_{3}^{-1}s_{1}s_{3}s_{2}^{-1}}s_{3}^{-1}s_{1}^{-1} \\
&= s_{3}\underline{s_{2}s_{2}^{-1}}s_{3}^{-1}s_{1}\underline{s_{3}s_{3}^{-1}}s_{1}^{-1} \\
&= \underline{s_{3}s_{3}^{-1}}\underline{s_{1}s_{1}^{-1}} \\
&= e
\end{align*}
\end{proof}

@@

\begin{thm}\todo{verify this}
\label{square_mutation_preserved}
The relations described in ~\ref{even_more_relations} are permuted (and hence preserved) after mutation at any vertex.
\end{thm}
\begin{proof}
This is what additionally needs to be checked in ~\ref{5.2 analog} by adding ~\ref{even_more_relations} in the cases corresponding to cycles with edges of weight 2 in the paper. I.e. it has to be checked in cases (b,c,d,e,f,g,h). It seems like a lot of casework, but there's a fair amount of symmetry to make it a bit easier, and I checked this in a few cases, and it seemed to work out. 
\end{proof}
